Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
update intro

Applying the same idea on big-step definitional interpreters, \citeauthor{darais2017abstracting} 
build abstract definitional interpreters (ADI) that are written in monadic style \cite{darais2017abstracting}
By changing the underlying
monads, the definition of interpreter has no change, but we can recover different semantics 
including the concrete semantics and various abstract semantics.

Broadly speaking, abstract abstract machines and abstract definitional interpreters are both
abstract interpreters. They are obtained by applying a combination of abstractions to their
concrete counterparts, abstract machines and definitional interperters, perspectively.
The relations between abstract machines, definitional interpreters, and monadic interpreters 
is intensively studied by Danvy and his collaborator in the past years 
\cite{Ager:2003:FCE:888251.888254, Danvy:2001:DW:773184.773202, danvy2004refocusing, Danvy:2008:DIP:1411204.1411206, AGER2004223, ager2005functional, Danvy:2006:RW:2171265.2171268}.

But in terms of their abstract semantic artifacts, 
the relations between small-step abstract abstract machines and big-step abstract 
definitional interpreters, and the question that how can we interdrive each other is not
well studied.
In this functional peral, we practical answer this question by presenting a series of 
syntactical transformations on the program from small-step abstract abstract machines 
to big-step abstract definitional interpreters.

\subsection{outline}

>>>>

Applying the same idea on big-step definitional interpreters, \citeauthor{darais2017abstracting} 
build abstract definitional interpreters (ADI) that are written in monadic style \cite{darais2017abstracting}.
One of the advantages of monadic interpreter is modular and composable.
By changing the underlying monads, the definition of interpreter has no change, 
but we can recover different semantics including the concrete semantics and various 
abstract semantics such as context-sensitivity and abstract garbage collection.

Broadly speaking, abstract abstract machines and abstract definitional interpreters are both
abstract interpreters. They are obtained by applying a combination of abstractions to their
concrete counterparts, abstract machines and definitional interperters, perspectively.
In concrete world, the relations among reduction semantics, abstract machines, definitional interpreters,
and monadic interpreters is intensively studied by Danvy and his collaborator in the past years 
\cite{Ager:2003:FCE:888251.888254, Danvy:2001:DW:773184.773202, danvy2004refocusing, Danvy:2008:DIP:1411204.1411206, AGER2004223, ager2005functional, Danvy:2006:RW:2171265.2171268, danvy2009towards, biernacka2009towards}.
The abstract machines implement structural operational semantics in continuation style, 
where the reduction contexts are defunctionalized continuations. One can derive definitional
interpreters by refunctionalizing the evaluation contexts of abstract machines; 
and by defunctionalizing the higher-order functions one may obtain abstract machines in the 
reversed direction.

But in terms of their abstract semantic artifacts, 
the relations between small-step abstract abstract machines and big-step abstract 
definitional interpreters, and the question that how can we interdrive each other is not
well studied.
The fundamental difference between concrete semantics artifacts and abstract semantics 
artifacts is non-determinism. In addition to insure termination, abstract semantics 
artifacts usually equipped with a cache of explored state that is guaranteed to reach 
the least fixed-point eventually.
In this functional peral, we practically answer the question and relate AAM and ADI 
by presenting a series of syntactical transformations on the program from
small-step abstract abstract machines to big-step abstract definitional interpreters.

\subsection{Outline}
